### 2014-04-16 doc/uist14/interaction.tex
pass the paper before noon submission
grammar in interaction

Infrared emitters are a good technology match since they emit light within a given angle, resulting in a cone in front of the emitter where the light is visible. LEDs with many different fields of view are commercially available. Each individual target that is equipped with IR detector can react to the signal. Such point to point communications enables us to achieve targeting without needing a map.
%% \bjoern{say something about receivers and how point to point connections enable us to leverage head orientation without needing a map.}

@@

Our augmentation to Google Glass adds a 940nm 5mm IR emitter (SFH 4545 from OSRAM Opto Semiconductors Inc.). The emitter is controlled by an additional microcontroller which communicates with Google Glass through Bluetooth radio. (see Figure~\ref{fig:glass}). In the following description, we use the succint term ``Glass'' to refer to this augmented hardware.

@@

\ben{no mention of target hardware yet. I have checked in an image of the targets ``targets.JPG'' in case we need.}

@@

{\bf Refine:} When disambiguation is needed, the user needs to make an explicit selection among the targets that within his view range. We have designed multiple refinement mechanisms -- all enable the user to select one from a subset of targets. The user confirms a current selection a tap. Since the purpose of this stage is to disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage. Again, a tap confirms a selection.

>>>>

Infrared emitters are a good technology match since they emit light within a given angle, resulting in a cone in front of the emitter where the light is visible. LEDs with many different fields of view are commercially available. Each individual target that is equipped with IR detector can react to the signal. Such point to point communication enables us to achieve targeting without needing a map.
%% \bjoern{say something about receivers and how point to point connections enable us to leverage head orientation without needing a map.}

@@

Our augmentation to Google Glass adds a 940nm 5mm IR emitter (SFH 4545 from OSRAM Opto Semiconductors Inc.). The emitter is controlled by an additional microcontroller which communicates with Google Glass through Bluetooth radio. (see Figure~\ref{fig:glass}). In the following description, we use the term ``Glass'' to refer to this augmented hardware.

@@

%% \ben{no mention of target hardware yet. I have checked in an image of the targets ``targets.JPG'' in case we need.}

@@

{\bf Refine:} When disambiguation is needed, the user must make an explicit selection among the targets within his view range. We have designed multiple refinement mechanisms -- all enable the user to select one from a subset of targets. The user confirms a current selection with a tap. Since the purpose of this stage is to disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage. Finally, a tap confirms a decision.
